sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-18 doc/paper.Rmd
Clean up refs
Start model description appendix

Take home, re-iterate paragraph?

@@

# Supplemental Materials

### Matern parameterization
<!-- EW: Because of space limits, I might suggest moving all this to the SI -->
The Matérn defines the covariance $\Phi \left( s_j, s_k \right)$ between spatial locations $s_j$ and $s_k$ as $\Phi\left( s_j,s_k \right) = \tau^2/\Gamma(\nu)2^{\nu - 1}
(\kappa d_{jk})^\nu K_\nu \left( \kappa d_{jk} \right)$,
<!-- TODO: paraphrase this to avoid self plagiarizing the synopsis report! -->
where $\tau^2$ represents the spatial variance, $\Gamma$ represents the Gamma function, $K_\nu$ represents the Bessel function, $d_{jk}$ represents the Euclidean distance between locations $s_j$ and $s_k$, and $\kappa$ represents
a scaling parameter that is estimated (REF).
The parameter $\nu$ controls the smoothness of the covariance function.
We set $\nu = 1$, which lets us take advantage of the Stochastic Partial Differential Equation (SPDE) approximation to the GMRF to greatly increase computational efficiency [@lindgren2011].

@@

Third more detailed example -- something like `pcod` or a fisheries dataset, with the Tweedie distribution, use of predict() function, and creating indices of abundance?

>>>>

<!-- Take home, re-iterate paragraph? -->

@@

<!--

@@

Third more detailed example -- something like `pcod` or a fisheries dataset, with the Tweedie distribution, use of predict() function, and creating indices of abundance?
-->
